Reconstructing Propositional Proofs in Type Theory

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ README ] Fixed a typo.
[ paper ] fixed intro in proof-reconstruction section.

The proof-reconstruction approach proposed consists of a series of
steps similar to the workflow presented~\cite{sultana2015}.  This
process is a translation from a source system to a target system. In
our case, the system of origin, the automatic theorem prover, is
\Metis; the target system is a proof-assistant, \Agda. We choose
\Agda, but another proof-assistant with the same support of type
theory and inductive types could be used.

@@

\input{sections/diagram.tex}
%  (see a description of \Agda for its main features in
% Section~\ref{sec:implementation}).
The overview of the proof-reconstruction is presented in
Fig.~\ref{fig:proof-reconstruction-workflow}. The process begins with
a \TPTP file that encodes a problem in \CPL. We use this file as the
input of the \Metis prover. If the problem is a theorem, \Metis
generates a derivation of the proof in \TSTP format.

>>>>

In this section, we describe one approach to reconstruct
propositional proofs. This reconstruction is a translation
process from a source system to the target system.
In our case, the system of origin, the automatic theorem prover, is
\Metis; the target system is a proof-assistant, \Agda. We choose
\Agda, but another proof-assistant with the same support of type
theory and inductive types could be used.

@@

\input{sections/diagram.tex}
The overview of the proof-reconstruction is presented as a workflow
in Fig.~\ref{fig:proof-reconstruction-workflow}. This workflow
follow the same basis of the proposed workflow presented
in~\cite{sultana2015}.

The process begins with a \TPTP file that encodes a problem in \CPL.
We use this file as the input of the \Metis prover. If the problem is
a theorem, \Metis generates a derivation of the proof in \TSTP
format.
